### 2015-07-20 Dissertation/part1.tex

\section{Ссылки} \label{sect1_2}
Сошлёмся на библиографию. Одна ссылка: \cite{Sokolov}. Две ссылки: \cite{Sokolov,Gaidaenko}. Много ссылок: \cite{Lermontov,Management,Borozda,Marketing,Constitution,FamilyCode,Gost.7.0.53,Razumovski,Lagkueva,Pokrovski,Sirotko,Lukina,Methodology,Encyclopedia,Nasirova,Berestova,Kriger}. И ещё немного ссылок: \cite{Article,Book,Booklet,Conference,Inbook,Incollection,Manual,Mastersthesis,Misc,Phdthesis,Proceedings,Techreport,Unpublished}.

>>>>

\section{Ссылки} \label{sect1_2}
Сошлёмся на библиографию. Одна ссылка: \cite[с.~54]{Sokolov}\cite[с.~36]{Gaidaenko}. Две ссылки: \cite{Sokolov,Gaidaenko}. Много ссылок: [\citenum{:/content/journals/10.1049/jiee-1.1923.0092}, с.~54; \citenum{Gaidaenko}, с.~36] \cite[с.~54]{Lermontov,:/content/journals/10.1049/jiee-1.1923.0092,Borozda} \cite{Lermontov,Management,Borozda,Marketing,Constitution,FamilyCode,Gost.7.0.53,Razumovski,Lagkueva,Pokrovski,Sirotko,Lukina,Methodology,Encyclopedia,Nasirova,Berestova,Kriger}. И ещё немного ссылок:\cite{samojlovich2004trehmernye, Shoji199895, Sinev2014} \cite{Article,Book,Booklet,Conference,Inbook,Incollection,Manual,Mastersthesis,Misc,Phdthesis,Proceedings,Techreport,Unpublished}.\cite{Li2007StressAnalysis,Gosele1999161, doi:10.1080/01932691.2010.513279, medvedev2006jelektronnye, ZAMM:ZAMM579, CEAT:CEAT581}
